Working with Poisson regression

### 2021-09-28 text/21/poisson-regression.Rmd
Added negative-binomial-regression.md

```

@@

+ Kilometres		Kilometres travelled per year
  + 1: < 1000
  + 2: 1000-15000
  + 3: 15000-20000
  + 4: 20000-25000
  + 5: > 25000
+ Zone		Geographical zone
  + 1: Stockholm, Göteborg, Malmö with surroundings
  + 2: Other large cities with surroundings
  + 3: Smaller cities with surroundings in southern Sweden
  + 4: Rural areas in southern Sweden
  + 5: Smaller cities with surroundings in northern Sweden
  + 6: Rural areas in northern Sweden
  + 7: Gotland
+ Bonus		No claims bonus. Equal to the number of years, plus one, since last claim
+ Make		1-8 represent eight different common car models. All other models are combined in class 9
+ Insured		Number of insured in policy-years
+ Claims		Number of claims
+ Payment		Total value of payments in Skr

>>>>

@@

+ Kilometres		Kilometres travelled per year
  + 1: < 1000
  + 2: 1000-15000
  + 3: 15000-20000
  + 4: 20000-25000
  + 5: > 25000
+ Zone		Geographical zone
  + 1: Stockholm, G?teborg, Malm? with surroundings
  + 2: Other large cities with surroundings
  + 3: Smaller cities with surroundings in southern Sweden
  + 4: Rural areas in southern Sweden
  + 5: Smaller cities with surroundings in northern Sweden
  + 6: Rural areas in northern Sweden
  + 7: Gotland
+ Bonus		No claims bonus. Equal to the number of years, plus one, since last claim
+ Make		1-8 represent eight different common car models. All other models are combined in class 9
+ Insured		Number of insured in policy-years
+ Claims		Number of claims
+ Payment		Total value of payments in Skr
